### 2023-08-22 application.tex
up

\begin{theorem}{}
{\sc Resilience} is decidable for VASS when $\Safe$ and $\Bad$ are semilinear sets.
\end{theorem}

@@

\begin{theorem}{}
{\sc Resilience} is decidable for lossy counter machines when $\Safe$ and $\Bad$ are semilinear sets.
\end{theorem}

@@

\begin{theorem}\label{RP VASS}
{\sc Resilience} is decidable for continuous VASS when $\Safe$ and $\Bad$ are definable in the existential theory of
the rationals with addition and order.
\end{theorem}

@@

\iffalse
\begin{figure}
\begin{center}
\begin{tabular}{ | l | c | c | c | r |}
\hline   \Safe~\Bad 
		& $\uparrow$~ $\downarrow$~ 
		 & $\downarrow$~ $\uparrow$~ 
 \\ \hline
   RP  & Decidable (Thm~\ref{down-up})   & Decidable (Thm~\ref{RP VASS})
    \\ \hline
   BRP   &  Decidable (Thm~\ref{down-up})  & Decidable (Thm~\ref{brp VASS})
    \\ \hline
      kRP       & Decidable (Thm~\ref{down-up}) & Decidable (Thm~\ref{brp VASS})
       \\ \hline
   sRP    	& Decidable (Thm~\ref{post srp})	 & ??
    \\ \hline
   BsRP     &  Decidable (Thm~\ref{ref ozkan})	 & ?? 
    \\ \hline
      ksRP        & Decidable (Thm~\ref{ref ozkan}) & ?? 
       \\ \hline

\end{tabular}
\end{center}
	\caption{Decidability results for VASS.}
\end{figure}
\fi

>>>>

\begin{theorem}{}
{\sc Resilience} is decidable for VASS when $\Safe$ 
%and $\Bad$ are semilinear sets.
is a semilinear set.
\end{theorem}

@@

\begin{theorem}{}
{\sc Resilience} is decidable for lossy counter machines when $\Safe$ 
%and $\Bad$ are semilinear sets.
is a semilinear set.
\end{theorem}

@@

\begin{theorem}\label{RP VASS}
{\sc Resilience} is decidable for continuous VASS when $\Safe$ 
%and $\Bad$ are
is
%s
definable in the existential theory of the rationals with addition and order.
\end{theorem}

@@
